---
title: "econ_assignment4"
author: "Jessica Jagdeo"
date: "May 28, 2019"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE}

library(tidyverse)
library(stargazer)

carbon_data <- read_csv("HW4Data.csv")

```

1. Model of marginal cost of abatement for each sector

```{r, visualizing data to find functional form, include = FALSE}

# Exploratory Graphs

sector_a <- ggplot(carbon_data, aes(x = Abatement, y = MC_A)) + 
  geom_point()
sector_a
# Looks linear enough...?


sector_b <- ggplot(carbon_data, aes(x = Abatement, y = MC_B)) + 
  geom_point()
sector_b
# idk

sector_c <- ggplot(carbon_data, aes(x = Abatement, y = MC_C)) + 
  geom_point()
sector_c
# Exponential...?

sector_d <- ggplot(carbon_data, aes(x = Abatement, y = MC_D)) + 
  geom_point()
sector_d
#idk 

```

```{r, estimating parameters, include = FALSE}

# Linear Regressions

# Sector A

sector_a_model <- lm(MC_A ~ Abatement, data = carbon_data)
sector_a_model

# Marginal cost of carbon abatement = 0.5768*(Abatement) - 8.6445


# Sector B
sector_b_model <- lm(MC_B ~ Abatement, data = carbon_data)
sector_b_model

# Marginal cost of carbon abatement = 0.1987*(Abatement) + 9.3177


# Sector C
sector_c_model <- lm(MC_C ~ Abatement, data = carbon_data)
sector_c_model

# Marginal cost of carbon abatement = 0.7838*(Abatement) - 11.6550


# Sector D
sector_d_model <- lm(MC_D ~ Abatement, data = carbon_data)
sector_d_model

# Marginal cost of abatement = 0.2599*(Abatement) + 9.6875

```

```{r, results = 'asis', echo = FALSE}

stargazer(sector_a_model, sector_b_model, sector_c_model, sector_d_model,
          type = "html",
          title = "Table 1. Linear Regression Models for Carbon Abatement from Sectors A, B, and C in Country X and Sector D in Country Y.", 
          dep.var.labels=c("Sector A", "Sector B", "Sector C", "Sector D")
          )

```



We have determined that linear regression models produce relatively adequate fits for the carbon emissions data from the sectors. 

Our linear regression models are:

Sector A: Marginal cost of carbon abatement = 0.5768*(Abatement) - 8.6445
Sector B: Marginal cost of carbon abatement = 0.1987*(Abatement) + 9.3177
Sector C: Marginal cost of carbon abatement = 0.7838*(Abatement) - 11.6550
Sector D: Marginal cost of abatement = 0.2599*(Abatement) + 9.6875

R^2 is the proportion of the variance in cost of abatement that is explained by the tons of carbon abatement. Basd on these models and their associated R^2, tons of carbon abatement significantly predicts marginal cost of abatement.

```{r, model fit, include = FALSE}

# Detailed model information

# Sector A

summary(sector_a_model)

# R^2 = 0.9104, p for model fit = 1.01e-08

# Basd on this model, Tons of carbon abatement significanly predicts marginal cost of abatement,  R^2 is the proportion of the variance in cost of abatement that is explained by the tons of carbon abatement. 91% of variance in cost is predictable by tons of carbon abatement and 9% of variance in cost is not predictable by tons.


# Sector B
summary(sector_b_model)

# R^2 = 0.5664, p = 0.0007672

# Secctor C
summary(sector_c_model)

# R^2 = 0.8752, p = 1.044e-07

# Sector D
summary(sector_d_model)
# R^2 = 0.5434, p = 0.001121


```

```{r, graphing abatement (cost) curves, echo = FALSE}

# Sector A

coeff_a <- coefficients(sector_a_model)
eq_sector_a <- paste0("y = ", coeff_a[2], "*x ", coeff_a[1])

equation_a_supply = function(x) {x*coeff_a[2] + coeff_a[1]}
curve(equation_a_supply, from = 0, to = 300, xlim = c(0,300), xaxs = "i", ylim = c(-20,250), yaxs = "i", xlab = "Carbon Abatement (Tons)", ylab = "Price ($) per Ton")


# Add sector B

coeff_b <- coefficients(sector_b_model)
eq_sector_b <- paste0("y = ", coeff_b[2], "*x ", coeff_b[1])

equation_b_supply = function(x) {x*coeff_b[2] + coeff_b[1]}
curve(equation_b_supply, from = 0, to = 300, add = TRUE, col = "blue")


# Add sector C

coeff_c <- coefficients(sector_c_model)
eq_sector_c <- paste0("y = ", coeff_c[2], "*x ", coeff_c[1])

equation_c_supply = function(x) {x*coeff_c[2] + coeff_c[1]}
curve(equation_c_supply, from = 0, to = 300, add = TRUE, col = "green")


# Add sector D

coeff_d <- coefficients(sector_d_model)
eq_sector_d <- paste0("y = ", coeff_d[2], "*x ", coeff_d[1])

equation_d_supply = function(x) {x*coeff_d[2] + coeff_d[1]}
curve(equation_d_supply, from = 0, to = 300, add = TRUE, col = "purple")

legend(1, 250, legend=c("Sector A", "Sector B", "Sector C", "Sector D"),
       col=c("black", "blue", "green","purple"), lty=1:1, cex=0.8)

```

2. Demand Curve

```{r}

# Find the intersection of the marginal cost curves with current emissions from each sector:


# Sector A

# Marginal cost of carbon abatement = 0.5768*(Abatement) - 8.6445

# Current emissions is 180 tons

0.5768*180-8.6445 # Equals $95.18

# Points: (180, 0) and (0, 95.18)

# Slope: -0.5287778

(95.18-0)/(0-180)

# Y-intercept: 95.18



# Sector B

# Marginal cost of carbon abatement = 0.1987*(Abatement) + 9.3177

# Current emissions are 200 tons

0.1987*200+9.3177 # Equals $49.06

# Points: (200, 0) and (0, 49.06)

# Slope: -0.2453

(49.06-0)/(0-200)

# Y-intercept: 49.06



# Sector C

# Marginal cost of carbon abatement = 0.78388(Abatement) - 11.6550

# Current emissions are 220 tons

0.78388*220-11.6550 # Equals $160.80

# Points: (220, 0) and (0, 160.80)

# Slope: -0.7309091

(160.80-0)/(0-220)

# Y-intercept: 160.80



# Sector D

# Marginal cost of abatement = 0.2599*(Abatement) + 9.6875

# Current emissions are 300 tons

0.2599*300+9.6875 # Equals $87.66

# Points: (300, 0) and (0, 87.66)

# Slope: -0.2922

(87.66-0)/(0-300)

# Y-intercept: 87.66

```

Demand curves for each sector:

Sector A: y = -0.5287778X + 95.18
Sector B: y = -0.2453X + 49.06
Sector C: y = -0.7309091X + 160.80
Sector D: y =  -0.2922X + 87.66

```{r, graphing the demand curves, echo = FALSE}

# Sector A

slope_a <- -0.5287778
y_int_a <- 95.18

equation_a_demand = function(x) {x*slope_a + y_int_a}
curve(equation_a_demand, from = 0, to = 200, xlim = c(0,300), xaxs = "i", ylim = c(0,200), yaxs = "i",yaxs = "i", xlab = "Carbon Emitted (Tons)", ylab = "Price ($) per Ton")


# Add Sector B 

slope_b <- -0.2453
y_int_b <- 49.06

equation_b_demand = function(x) {x*slope_b + y_int_b}
curve(equation_b_demand, from = 0, to = 300, add = TRUE, col = "blue")


# Add Sector C

slope_c <- -0.7309091
y_int_c <- 160.80

equation_c_demand = function(x) {x*slope_c + y_int_c}
curve(equation_c_demand, from = 0, to = 300, add = TRUE, col = "green")


# Add Sector D

slope_d <- -0.2922
y_int_d <- 87.66

equation_d_demand = function(x) {x*slope_d + y_int_d}
curve(equation_d_demand, from = 0, to = 300, add = TRUE, col = "purple")

legend(150, 200, legend=c("Sector A", "Sector B", "Sector C", "Sector D"),
       col=c("black", "blue", "green","purple"), lty=1:1, cex=0.8)

```

3. Country X Abatement

a. Cap on carbon

```{r, total cost of meeting target if each county reduces by 100 tons, include = FALSE}

# Sector A
# Marginal cost of carbon abatement = 0.5768*(Abatement) - 8.6445
0.5768*(100) - 8.6445
# Marginal cost = $49.0355
# Cost (area under the curve) = $2019.55 
# To find the area under the curve, the equation is 0.5*100(base)*marginal cost(height)
sectorA_totalcost <- 2019.55 

# Sector B
# Marginal cost of carbon abatement = 0.1987*(Abatement) + 9.3177
0.1987*(100) + 9.3177
# Marginal cost = $29.1877
# Cost = $1925.27 
sectorB_totalcost <- 1925.27

# Sector C
# Marginal cost of carbon abatement = 0.7838*(Abatement) - 11.6550
0.7838*(100) - 11.6550
# Marginal cost = 66.725
# Cost = $2753.5 
sectorC_totalcost <- 2753.5

# Total cost for Country X
# $6698.32 

countryX_totalcost3A <- sectorA_totalcost+sectorB_totalcost+sectorC_totalcost


# No tax revenue generated in this scenario

```


b. Tax on Carbon

```{r, add equations horizontally, include = FALSE}

# Rearrange equations

# Sector A: Cost of carbon abatement = 0.5768*(Abatement) - 8.6445
# Abatement = 1.733703*(cost) + 14.987
      # non-rounded numbers just in case:
      a1 <- 1/0.5768
      a2 <- 8.6445/0.5768


# Sector B: Cost of carbon abatement = 0.1987*(Abatement) + 9.3177
# Abatement = 5.032713*(cost) -  46.89331
      # non-rounded numbers
      b1 <- 1/0.1987
      b2 <- -9.3177/0.1987


# Sector C: Cost of carbon abatement = 0.7838*(Abatement) - 11.6550
# Abatement = 1.275836*(cost) + 14.86986
      #non-rounded numbers
      c1 <- 1/0.7838
      c2 <- 11.6550/0.7838

      

# Add them up for aggregate equation
      
# Abatement = (a1 + b1 + c1)*cost + (a2 + b2 + c2)
      m1 <- (a1 + b1 + c1) # 8.042251
      y <- (a2 + b2 + c2) # -17.03644
# Abatement = 8.042251*(cost) - 17.03644
      
```

```{r, find tax price, include = FALSE}

# Rearrange aggregate equation to y = mx + b form

      m <- 1/m1 # 0.12343
      b <- -y/m1 # 2.11837

# Marginal cost of abatement = 0.12343*(Abatement) + 2.11837
      
      
# Plug in abatement amount
tax <- 0.12343*(300) + 2.11837
# Marginal cost of abating 300 tons = $39.14737
# Tax should be set at $39.15

```

```{r, find quantity each sector will abate at tax price, include = FALSE}

# Sector A
# 39.14737 = 0.5768*(Abatement) - 8.6445
sectorA_abatement3B <- (tax + 8.6445) / 0.5768
# Abatement = 82.85692 tons


# Sector B
# 39.14737 = 0.1987*(Abatement) + 9.3177
sectorB_abatement3B <- (tax - 9.3177) / 0.1987
# Abatement = 150.1242 tons


# Sector C
# 39.14737 = 0.7838*(Abatement) - 11.6550
sectorC_abatement3B <- (tax + 11.6550) / 0.7838
# Abatement = 64.81548 tons

```

```{r, cost to each sector, include = FALSE}

# Integrate from 0 to actual abatement amount for each sector then add how much taxes they have to pay to find total cost:

# Integrate from 0 to 82.85692
sectorA_totaltax3B <- ((180 - sectorA_abatement3B)*tax)
# Add tax
sectorA_totalcost3B <- 1263.69 + sectorA_totaltax3B
# Total cost to Sector A under tax is $5066.59

# Integrate from 0 to 
sectorB_totaltax3B <- ((200 - sectorB_abatement3B)*tax)
# Add tax
sectorB_totalcost3B <- 3637.89 + sectorB_totaltax3B
# Total cost to Sector B under tax is $5590.40


# Integrate from 0 to
sectorC_totaltax3B <- ((220 - sectorC_abatement3B)*tax)
# Add tax
sectorC_totalcost3B <- 651.284 + sectorC_totaltax3B
# Total cost to Sector C under tax is $6726.35

```

```{r, total cost of meeting target under a tax, include = FALSE}


# Total cost for country X is sectos added together minus tax revenue because tax goes to the country's govnerment
countryX_totalcost3B <- (sectorA_totalcost3B + sectorB_totalcost3B + sectorC_totalcost3B) - (sectorA_totaltax3B + sectorB_totaltax3B + sectorC_totaltax3B)

# Total cost of meeting target under tax for Country X is $5552.86

```

```{r, tax revenue generated in Country X, include = FALSE}

countryX_taxrev3B <- 300*tax

# Tax revenue generated under tax of $39.15 is $11,744.21

```


C. Cap and trade.

```{r, cap and trade amounts for each sector, include = FALSE}

# Sector A
# 39.14737 = 0.5768*(Abatement) - 8.6445
sectorA_captrade3C <- 100 - ((tax + 8.6445) / 0.5768)
# Sector A needs to buy 17.143 credits to actually abate 100 tons


# Sector B
# 39.14737 = 0.1987*(Abatement) + 9.3177
sectorB_captrade3C <- 100 - ((tax - 9.3177) / 0.1987)
# Sector B abated more than 100 tons, so it can sell 50.124 credits


# Sector C
# 39.14737 = 0.7838*(Abatement) - 11.6550
sectorC_captrade3C <- 100 - ((tax + 11.6550) / 0.7838)
# Sector C needs to buy 35.185 credits to actually abate 100 tons

```

```{r, cost and benefits to each sector, include = FALSE}

# Sector A emits 97.14308 tons (180 - 82.856917)
# sector B emits 49.87584 tons (200 - 150.12415)  THIS SHOULD BE EMITS 48. WE PROBS HAVE A ROUNDING PROBLEM SOMEWHERE 
# Sector C emits 155.1845 tons (220 - 64.815476)

# Sector A is given 80 permits
# Sector B is given 100 permits
# Sector C is given 120 permits

# Sector A needs 17 permits
# Sector B sells 52 permits
# Sector C needs 35 permits


# Add up cost under curve (integral from 0 to abatement level) and value of trade to get total cost 

sectorA_permit <- 1263.69 + (tax*17)
# Sector A will pay $665.51 for 17 permits, leading to a total cost of 1929.20

sector_B_permit <- 3637.89 - (tax*52)
# Sector B will receive $1996.52 for 51 permits sold, leading to a total of 1602.23

sectorC_permit <- 651.284 + (tax*35)
# Sector C will pay $1370.16 for 35 permits sold, leading to a total cost of 2021.44

```

```{r, cost country as a whole, include = FALSE}

countryX_totalcost3C <- (sectorA_permit + sectorC_permit + sector_B_permit)

# Total cost to country X under cap and trade is $5552.86

# This is the same total cost as Country X under a carbon tax, but the individual sectors do better under cap and trade

```

No tax revenue in a cap and trade system

4. Again, without any co-benefits, suppose that country Y (which only has one carbon-emitting sector, D) has no obligation to reduce its emissions. Country X asks country Y to enter the country X carbon
market. Doing so would require country Y to put a cap on carbon emissions at its current level of
emissions (300 tons), but would then allow country Y to sell carbon offsets to sectors A, B, or C. Are
there any incentives for country Y to enter country X’s carbon market and to thus place a voluntary cap on its emissions? Are there any incentives for country X to try to attract country Y into its market?

```{r, include = FALSE}

# Re-arrange sector D abatement curve in terms of x:
# For Sector D: Marginal cost of abatement = 0.2599*(Abatement) + 9.6875
# y = 0.2599X + 9.6875
1/0.2599
-9.6875/0.2599
# x = 3.847634y - 37.27395

# Add Sectors A, B, C agg. supply curve to Sector D's supply curve:
# For Sector D: x = 3.847634y - 37.27395
# For Sectors A, B, C: x = 8.042251y - 17.03644
3.847634 + 8.042251
- 37.27395 - 17.03644
# Agg. supply curve w/ A, B, C, D: x = 11.88988y - 54.31039

# Rearrange agg. supply curve in terms of y:
1/11.88988
54.31039/11.88988
# Rearranged equation: y = 0.08410515X + 4.567783

```

```{r, include = FALSE}

# New tax w/ Sector D involved:
# y = 0.08410515X + 4.567783
tax4 <- ((0.08410515 * 300) + 4.567783)
# New tax w/ Sector D is $29.80

```

```{r, include = FALSE}

# Abatement under this scenario:

# Sector A
sectorA_abatement4 <- ((tax4 + 8.6445) / 0.5768)
# Sector A will abate 66.65 tons
# Sector A is now emitting 113.35 tons
# Sector A needs to buy 34 credits


# Sector B
sectorB_abatement4 <- ((tax4 - 9.3177) / 0.1987)
# Sector B will abate 103.07 tons
# Sector B is now emitting 96.93
# Sector B will sell 4 credits


# Sector C
sectorC_abatement4 <- ((tax4 + 11.6550) / 0.7838)
# Sector C will abate 52.88 tons 
# Sector C is now emitting 167.12
# Sector C needs to buy 48 credits

# Sector D
sectorD_abatement4 <- ((tax4 -9.6875)/0.2599)
# Sector D will abate 77.38 tons
# Sector D  is now emitting 222.62
# Sector D will sell 78 credits

```

Country X would want Country Y to join the carbon market because the marginal cost of abatement for all four sectors is less than the marginal cost of abatement for Country X (Sectors A, B, and C).

Country Y would want to join the carbon market because it would be able to sell 78 permits to Sectors A and C, therefore making money. 


5. Now assume that every ton of carbon emissions creates 1 ton of local air pollution. Local air pollution causes economic damages (health, environmental, etc.), but only in the country in which it is emitted. Assume there are no local air pollution regulations in either country X or country Y.

a. In a carbon cap and trade market that only covers sectors in country X, how much local air pollution would you expect in country X? In country Y?

*In Country X, we expect 300 tons of local air pollution. In Country Y, we expect 300 tons of local air pollution as well.* 

b. If country Y enters the carbon market for country X (as in question 4 above), how much local
pollution will there be in country X and country Y?

*In Country X, we expect 378 tons of local air pollution. In Country Y, we expect 223 tons of local air pollution.*

c. What advice can you give country X and country Y about the desirability of allowing
international trade of carbon emissions credits?

*It is econonmically desirable for Country X and Country Y to engage in carbon trading within this market system. However, it is important to note that in terms of local air pollution, carbon trading may not be desirable because this trading increases air pollution from Country X.*

